ZCB Pricing

### 2018-07-25 ZCB Pricing .Rmd
Removed my MC chunk

```{r 2}
# Monte Carlo Simulation

monte_carlo <- function(alpha =0.08, beta=0.8, sigma=0.005, t=0, T=1, r=0.08, n=1000, s=100){
  # s = number of sub-intervals
  # n = number of simulation trials

  dt <- T/s
  sim_path <- matrix(NA,nrow = n, ncol = 1) # matrix to store simulated path integrals
  sim_r <- NULL # vector to store rates on the path

  for (d in 1:n){
    sim_r[1] <- r
    for (j in 2:s){
      mu <- alpha/beta + exp(-beta*dt)*(sim_r[j-1] -alpha/beta)
      sd <- sqrt((sigma^2/(2*beta))*(1 -exp(-2*beta*(dt))))
      sim_r[j] <- rnorm(1,mu,sd)
    }

    int <- dt*(sum(sim_r)) # integral of path
    sim_path[d,1] <- exp(-int) # bond price of path

  }
  mean(sim_path) # empirical expectation of bond price using all paths
}

```{r}

# Another Version of the MOnte Carlo simulations
Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

@@

```{r}
#################################################################################
# Moment matching
#################################################################################

@@

```{r}
#################################################################################
# Control Variates
#################################################################################

@@

```{r}

@@

```{r 4}
# Explicit Method

@@

```{r 5}

@@

```{r 6}
# Crank-Nicholson Method

@@

```{r 7}
# Modified Fully Implicit Method
```

```{r 8, echo = FALSE}
# Comparison of results
# Varying short rates

@@

var <- sum(compare_mat[,8])/9

library(knitr)
kable(compare_mat,align = "c")

>>>>

```{r 2}
#################################################################################
# Crude Monte Carlo
#################################################################################
Crude_Monte_Carlo=function(alpha =0.08,beta=0.8,sigma=0.005,T=1,r0 = 0.08,n=1000,s=100){

@@

```{r 4}
#################################################################################
# Moment matching
#################################################################################

@@

```{r 5}
#################################################################################
# Control Variates
#################################################################################

@@

```{r 6}

#======================================================================================
# Doing some plots

@@

```{r 7}
# Explicit Method

@@

```{r 8}

@@

```{r 9}
# Crank-Nicholson Method

@@

```{r 11}
# Modified Fully Implicit Method
```

```{r 12, echo = FALSE}
# Comparison of results
# Varying short rates

@@

# library(knitr)
# kable(compare_mat,align = "c")
